ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
replaced short title
fix character

    \title[short Title]{ODGI: scalable tools for pangenome graphs}
    \author[Sample \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

@@

    \section{Discussion}
    We implemented a tool suite, \odgi\, which is simple to work with to analyse and manipulate pangenome graphs at a
    population scale. \odgi\'s path implementation allows working with graphs of any complexity, without particular
    limitations. We have demonstrated that \odgi\ tools efficiently perform with pangenome graphs embedding full human
    chromosomes. \odgi\ is not only a tool suite but also a library, already used in pangenome graphs building
    (\citep{pggb}) and normalization (\citep{smoothxg}). Furthermore, users can add new tools, exploiting ODGI as a
    framework where to implement algorithms working on variation graphs. Therefore, \odgi\ offers an efficient and
    extendable suite of tools ready for the upcoming challenges in the analyses of hundreds of genomes at a gigabase
    scale that characterize the pangenomic era.

>>>>

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Sample \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

@@

    \section{Discussion}
    We implemented a tool suite, \odgi\, which is simple to work with to analyse and manipulate pangenome graphs at a
    population scale. ODGI's path implementation allows working with graphs of any complexity, without particular
    limitations. We have demonstrated that \odgi\ tools efficiently perform with pangenome graphs embedding full human
    chromosomes. \odgi\ is not only a tool suite but also a library, already used in pangenome graphs building
    (\citep{pggb}) and normalization (\citep{smoothxg}). Furthermore, users can add new tools, exploiting ODGI as a
    framework where to implement algorithms working on variation graphs. Therefore, \odgi\ offers an efficient and
    extendable suite of tools ready for the upcoming challenges in the analyses of hundreds of genomes at a gigabase
    scale that characterize the pangenomic era.
